\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-05-15 paper/ms.tex
showresults figures

\section{Running models}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/regression_lines.pdf}
\caption{Regression lines drawn from the posterior.
\label{fig:regression_lines}}
\end{figure}

@@

\section{Implementing models}\label{sec:models}
The ``classic'' method of implementing models in \pkg{DNest4} is by
writing a \proglang{C++} class, an object of which represents a
point in your parameter space.
To demonstrate, consider a simple linear regression situation where the
sampling distribution is
\begin{align}
y_i | m, b, \sigma &\sim \textnormal{Normal}(mx_i + b, \sigma^2)
\end{align}
and the priors are
\begin{align}
m &\sim \textnormal{Normal}(0, 1000^2)\\
b &\sim \textnormal{Normal}(0, 1000^2)\\
\ln\sigma &\sim \textnormal{Uniform}(-10, 10)
\end{align}
These are naive diffuse priors and we do not claim any special status for them.

>>>>

\section{Running models}
To demonstrate \pkg{DNest4},
we will use a simple linear regression example where the
sampling distribution is
\begin{align}
y_i | m, b, \sigma &\sim \textnormal{Normal}(mx_i + b, \sigma^2)
\end{align}
and the priors are
\begin{align}
m &\sim \textnormal{Normal}(0, 1000^2)\\
b &\sim \textnormal{Normal}(0, 1000^2)\\
\ln\sigma &\sim \textnormal{Uniform}(-10, 10).
\end{align}
These are naive diffuse priors and we do not claim any special status for them.
This model was implemented in \proglang{C++}
(see Section~\ref{sec:models} for details) and is included in the
code/Examples/StraightLine subdirectory.

\begin{figure}[ht!]
\begin{minipage}{0.5\textwidth}
\includegraphics[width=8cm]{figures/fig1.pdf}
\caption{\label{fig:fig1}}
\end{minipage}
\begin{minipage}{0.5\textwidth}
\includegraphics[width=8cm]{figures/fig2.pdf}
\caption{\label{fig:fig2}}
\end{minipage}
\end{figure}

\begin{figure}[ht!]
\begin{minipage}{0.5\textwidth}
\includegraphics[width=8cm]{figures/fig3.pdf}
\caption{\label{fig:fig3}}
\end{minipage}
\begin{minipage}{0.5\textwidth}
\includegraphics[width=8cm]{figures/regression_lines.pdf}
\caption{Regression lines drawn from the posterior.
\label{fig:regression_lines}}
\end{minipage}
\end{figure}

@@

\section{Implementing models}\label{sec:models}
The ``classic'' method of implementing models in \pkg{DNest4} is by
writing a \proglang{C++} class, an object of which represents a
point in your parameter space.
